Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-08 article/article.tex
Commit 2024-09-08 13:09

For the detection of CE cases, we established a baseline of irradiance
above which we characterized each data point as an enhancement event and
calculated the over irradiance (OI). The OI is defined as the irradiance
difference of the measured one-minute GHI from the
\(\text{GHI}_\text{ref}\) corresponding to cloud-free atmosphere. First,
we used a simple approach for the determination of
\(\text{GHI}_\text{ref}\): The Haurwitz's model \citep{Haurwitz1945},
which is a simple clear sky radiation model and was already adjusted and
applied to our data \citep{Natsis2023}. We created a threshold by using
an appropriate relative and/or an additional constant offset. The
initial results showed that we can detect a big portion of the actual CE
events. However, by inspecting the daily plots of irradiance it became
evident that changes in atmospheric conditions introduced numerous false
positive or false negative results. The main reason for these
discrepancies is the variability of the effects of aerosols and water
vapor which were not considered in the simple method. To produce a more
representative reference we included the effects of these factors using
a radiative transfer model (RTM). The applied methodology is discussed
in section\nobreakspace{}\ref{rtmcs}.

@@

>>>>

For the detection of CE cases, we established a baseline of irradiance
above which we characterized each data point as an enhancement event and
calculated the over irradiance (OI). The OI is defined as the irradiance
difference of the measured one-minute GHI from the
\(\text{GHI}_\text{ref}\) corresponding to cloud-free atmosphere. First,
we used a simple approach for the determination of
\(\text{GHI}_\text{ref}\): The Haurwitz's model \citep{Haurwitz1945},
which is a simple clear sky radiation model and was already adjusted and
applied to our data \citep{Natsis2023}. We created a threshold by using
an appropriate relative and/or an additional constant offset. The
initial results showed that we can detect a big portion of the actual CE
events. However, by inspecting the daily plots of irradiance, it became
evident that changes in atmospheric conditions introduced numerous false
positive or false negative results. The main reason for these
discrepancies is the variability of the effects of aerosols and water
vapor which were not considered in the simple method. To produce a more
representative reference we included the effects of these factors using
a radiative transfer model (RTM). The applied methodology is discussed
in section\nobreakspace{}\ref{rtmcs}.

@@

\textbf{to edit}

The variable parameters of LUT consists of the month along with the
relevant seasonal atmospheric profile, the climatological values of the
alpha, beta parameters of the Ångström equation for 500nm derived from
the 340nm, the WC, with the perturbation as described above, and the SZA
of the simulation.

For the application of the LUT, to account for the Sun's variability, in
our one-minute GHI measurements, we adapted each modeled value by
scaling the model's input spectrum integral, to the corresponding TSI,
provided by NOAA \citep{Coddington2005}. Also, we account for the effect
of the Earth -- Sun distance on the irradiance, by using the distance
calculated by the Astropy \citep{AstropyCollaboration2022} software
library. As needed, we interpolate the resulting irradiances to the SZA
of our measurements. For each period of the year, we used the
appropriate atmospheric profile (afglms or afglmw). Finally, we
calculated the cloud-free irradiance value at the horizontal plane. With
this method, the modeled cloud-free irradiances schemes can be directly
compared to each measured one-minute value of GHI.
